%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Jivitesh Poojary 01/2021 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=1cm,right=8cm,marginparwidth=6cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Jivitesh Poojary$\tiny_{Jee-Vee-Taysh}$}
\tagline{}
%\photo{2cm}{jivipic}
\personalinfo{
   % \printinfo{\faBirthdayCake}{29 ans}
    \email{jivitesh.poojary@gmail.com}
    \phone{+1 720 705 0503}
    % \mailaddress{10400, Aspect Apartments}
    \location{Denver, Colorado, USA \emph{[Open to relocation]}} \\
    % \homepage{http://jivitesh-poojary.github.io/} \\
    \linkedin{www.linkedin.com/in/jivitesh-poojary/}
    \github{www.github.com/jivitesh-poojary}
    \twitter{www.twitter.com/jiviteshpoojary}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Formation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Machine Learning Engineer - II}{Dish Network }{Oct 2018 -- Present}{Denver, Colorado}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Created a spark application that generates viewership forecasts on a quarter and week level using Pandas UDF and Facebook Prophet. Millions of forecasts are generated in a batch mode on EMR and stored in S3. The model performs better over a heuristic based system 80\% of the time and is expected to produce a positive cash flow of \$16.4 M over 3 years. Recognized with `CIO Award` for this effort.}
    \item[--]   \small{Designed and deployed an ad slot capacity forecasting tool on AWS. Created a RESTful API service for the forecasts and integrated it with a front-end built in Dash. This tool helps the business with TV advertisement deal pacing and obtain insights on future ad inventory, thereby helping us increase revenue by \$75,000 per week.}
    \item[--]   \small{Developed a model to predict the propensity of the customers to churn within the next business cycle. With feature engineering and dimensionality reduction, maintaining levels of Precision and Recall decreased training time by 80\% over raw data. Improved model performance by 5\% by including customer geo-location data. The model helped us identify 40\% more customers over a control group.}
\end{itemize}

%\medskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{Machine Learning Engineer}{Vanguard}{Aug 2018 -- Oct 2018}{Charlotte, North Carolina}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]  \small {Using AWS labs Deequ, CloudWatch and QuickSight developed a monitoring system on few datasets. This initiative helped the Data Scientists with catching data drift on some model input variables before model performance deteriorated.}
    \item[--]  \small {Helped the team of Data Engineers and Big Data Architects to come up to speed with concepts in Anomaly Detection.}
\end{itemize}

%\medskip

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Senior Data Analyst}{Government of Maharashtra}{Sept 2015 -- July 2016}{Mumbai, India}

\begin{itemize}
   \setlength{\itemindent}{0.5em}
   \item[--]  \small {Analyzed economic indicator data and helped create a survey report outlining the impact of land allocation policy changes done by all major states in India after 2010.}
   \item[--]  \small {Examined the existing analytics infrastructure at a state level public sector organization. Presented solutions on improving the data collection processes and migration to Gov cloud.}
\end{itemize}

%\medskip

%%%%%%%%%%%%%
%Experience 4
%%%%%%%%%%%%%

\cvevent{Data Engineer}{Deloitte Digital}{Jan 2014 -- Sept 2015}{Mumbai, India}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Designed and developed applications on the Force.com platform. Using a CPQ process formulated product pricing strategies and technical implementations for sales teams and improved quoting and contracting system for legal team.}
    \item[--]   \small{Collaborated with multiple data engineering teams to migrate data and ETL processes from an on-prem environment to the Salesforce Cloud. Awarded ‘Outstanding Employee Award’ for this project}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience Professionnelles
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Education}

%%%%%%%%%%%%%
%Formation 1
%%%%%%%%%%%%%

\cvevent{Master of Science - Data Science }{School of Informatics, Computing, and Engineering (SICE), Indiana University }{Aug 2016 -- May 2018}{Bloomington, Indiana}

\medskip

%%%%%%%%%%%%%
%Formation 2
%%%%%%%%%%%%%

\cvevent{Bachelor of Technology - Information Technology }{Veermata Jijabai Technological Institute (VJTI), Mumbai University }{July 2009 -- May 2013}{Mumbai, India}

\medskip


\end{document}